Distributional Trees for Circular Data

### 2019-01-31 pkg/disttree/inst/IWSM2019/abstract_IWSM2019.tex
Merge conflict
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2418 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 93087120b186ea5ca5a2be2365f3a0f4085b54f5
Update application to old version
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2419 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: efa02a275e938382e721d33da40155e69efa2e74

%\begin{figure}
%\includegraphics[height = 0.5\textheight,angle=90,origin=c]{circtree_plot_big.pdf}
%\caption{\label{fig:circtree} Fitted distribution tree for a circular response employing the von Mises %distribution.}\label{fig:tree}
%\end{figure}

Wind is a classical circular quantity and accurate forecasts of wind direction
are of great importance for decision making processes and risk management,
e.g., in air traffic management and renewable energy production. As a suitable
and useful application of circular regression trees, we therefore forecast the
wind direction at the airport of Innsbruck. As potential split variables we
employ several 1-hourly lagged observed weather variables (e.g., wind speed,
relative humidity, pressure) and derived spatial and temporal difference of
these lagged observations.

Innsbruck lies with the west-east oriented Inn Valley with an approx. 2300\,m
high mountain ridge on the northern side and with the south-north oriented Wipp
Valley between the approx. 2300\,m high mountains on the southern side.
Therefore, skill full covariates are pressure differences along the Inn Valley
as indices for up- or down-valley winds. For the typical dry gap wind coming
from the south, indices are, e.g. low relative humidity or temperature
differences between Innsbruck and stations up the Wipp Valley.

The weather station of interest, Innsbruck Airport, lies at the bottom of the
Inn Valley, a deep mountain valley in the Eastern European Alps orientated
parallel to the Alpine crest. At Innsbruck, the Inn Valley is bordered in the
North with a approx. 2300\,m high mountain ridge and opens in the South into
the crest-perpendicular Wipp Valley. Therefore, mainly three different wind
regimes exist: Up-valley winds blowing from the valley mouth towards the upper
valley (from east to west), down-valley winds blowing in the direction of the
valley mouth (from west to east), and dry and warm downslope winds blowing
across the Alpine crest along the Wipp Valley towards Innsbruck (from
south-east to north-west).

@@

%\bigskip
\section{Outlook}

>>>>

%\begin{figure}
%\includegraphics[height = .5\textheight,angle=90,origin=c]{circtree_plot_big.pdf}
%\caption{Fitted distribution tree for a circular response employing the von Mises distribution.}
%\label{fig:tree}
%\end{figure}

Wind is a classical circular quantity and accurate forecasts of wind direction
are of great importance for decision making processes and risk management,
e.g., in air traffic management and renewable energy production. As a suitable
and useful application of circular regression trees, we therefore forecast the
wind direction at the airport of Innsbruck. As potential split variables we
employ several 1-hourly lagged observed weather variables (e.g., wind
direction, wind speed, relative humidity, pressure) and derived spatial and
temporal difference of these lagged observations.

The weather station of interest, Innsbruck Airport, lies at the bottom of the
Inn Valley, a deep mountain valley in the Eastern European Alps orientated
parallel to the Alpine crest. At Innsbruck, the west-east aligned Inn Valley is bordered in the
North with a approx. 2300\,m high mountain ridge and opens in the South into
the crest-perpendicular Wipp Valley. Therefore, mainly three different wind
regimes exist: Up-valley winds blowing from the valley mouth towards the upper
valley (from east to west), down-valley winds blowing in the direction of the
valley mouth (from west to east), and dry and warm downslope winds blowing
across the Alpine crest along the Wipp Valley towards Innsbruck (from
south-east to north-west).

@@

\section{Outlook}
